---
title: "UCL Maths & Stats"
author: Gianluca Baio
institute: "[Department of Statistical Science](https://www.ucl.ac.uk/statistics/) | University College London"
params: 
   conference: "Martingale Foundation Open Day"
   location: " Royal Institution, London"
   date: 8 December 2023
   short_title: "Martingale Open Day"
   center_footer: TRUE
   slides_url: ""
date: 
output:
  xaringan::moon_reader:
    # This allows to use the local 'remarks' installation, obtained by running 'xaringan::summon_remarks()'
    # chakra: libs/remark-latest.min.js
    includes: 
       in_header: "assets/latex_macros.html" 
       ## This line adds a logo based on the format selected in the file 'assets/THEME/include_logo.html'
       ## NB: the actual options (eg placement of the logo and actual logo file) can be changed there
       ## There's also a script to manipulate the colouring scheme for the UCL logo (from a basic black/white one)
       after_body: "assets/ucl-stats/insert-logo.html"
    seal: false
    yolo: no
    lib_dir: libs
    nature:
      beforeInit: ["https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: yes
      countIncrementalSlides: no
      ratio: '16:9'
      titleSlideClass:
      - center
      - middle
    self_contained: false 
    css:
    - "assets/fonts.css"
    - "assets/ucl-stats.css"
    - "assets/common.css"
---

```{r echo=F,message=FALSE,warning=FALSE,comment=NA}
# Sources the R file with all the relevant setup and commands
source("assets/setup.R")

# Stuff from 'xaringanExtra' (https://pkg.garrickadenbuie.com/xaringanExtra)
# This allows the use of panels (from 'xaringanExtra')
xaringanExtra::use_panelset()
# This allows to copy code from the slides directly
xaringanExtra::use_clipboard()
# This freezes the frame for when there's a gif included
xaringanExtra::use_freezeframe()
# Can also add the scribbling function to the slides
# xaringanExtra::use_scribble()
# Can also add a search box
# xaringanExtra::use_search(show_icon = TRUE)

# Defines the path to the file with the .bib entries (in case there are references)
bibfile=ReadBib("~/Dropbox/Perso/Office/CV/mypubs.bib",check = FALSE)
```

```{r title-page, child="assets/title-page.Rmd"}
```

# University College London

<style>
.font125 {
font-size: 125%;
}
.left-35 {
  width: 35%;
  height: 92%;
  float: left;
}
.left-35 h2, .left-column h3 {
  color: #035AA699;
}
.left-35 h2:last-of-type, .left-column h3:last-child {
  color: #035AA6;
}
.right-65 {
  width: 60%;
  float: right;
  padding-top: 0em;
}
</style>

`r vspace("50px")`
.left-35[
`r vspace("30px")`
`r include_fig("ucl-portico-ranbow.jpg",width="100%")`
]

.right-65[
.font125[
- UCL is a part of the [University of London](https://london.ac.uk/)

   - UoL is a **federation** of 17 independent member institutions of outstanding global reputation

`r vspace("30px")`
   
- We are a multidisciplinary university in its own right

- Founded in 1826 (you'll be bang in the middle of the bicentenary celebrations!)

- The first English university to admit Jewish, Catholics, Non-conformists faiths, Women, ...

   - [Thomas Arnold](https://en.wikipedia.org/wiki/Thomas_Arnold) referred to us as "*that Godless institution in Gower Street*".

`r vspace("30px")`

- The first globally to have departments of **Statistics**, Economics, Modern Languages, ...

]
]

---

count: false
# University College London

`r vspace("50px")`
.left-35[
`r vspace("30px")`
`r include_fig("ucl-portico-ranbow.jpg",width="100%")`
]

.right-65[
.font125[
- UCL is a part of the [University of London](https://london.ac.uk/)

   - UoL is a **federation** of 17 independent member institutions of outstanding global reputation

`r vspace("30px")`
   
- We are a multidisciplinary university in its own right

- Founded in 1826 (you'll be bang in the middle of the bicentenary celebrations!)

- The first English university to admit Jewish, Catholics, Non-conformists faiths, Women, ...

   - [Thomas Arnold](https://en.wikipedia.org/wiki/Thomas_Arnold) referred to us as "*that Godless institution in Gower Street*".

`r vspace("30px")`

- The first globally to have departments of **Statistics**, Economics, Modern Languages, ...

`r vspace("20px")`
- ... And one of the original Martingale's partners
]
]

---

# UCL Department of Mathematics

ADD FROM CHRISTIAN/HELEN HERE



---

# UCL Department of Statistical Science

<style>
.font115 {
font-size: 115%;
}
</style>

.left-column[
`r include_fig("UCL_Stats_logo.jpeg",width="100%")`
]

.font115[
.right-column[
`r vspace("-30px")`
## History

- First ever Department of Statistics in the world; founded in 1911

- Its first head was Karl Pearson (more on this later...)

- Now one of the largest in the UK

]
]

---

count: false
# UCL Department of Statistical Science

.left-column[
`r include_fig("UCL_Stats_logo.jpeg",width="100%")`
]

.font115[
.right-column[
`r vspace("-30px")`
## History

- First ever Department of Statistics in the world; founded in 1911

- Its first head was Karl Pearson (more on this later...)

- Now one of the largest in the UK


## Active in research

- Wide variety of statistical research

- 90% of research outputs submitted in the "Research Excellence Framework" (REF; 2021) ranked as "**internationally excellent**"

- We've improved markedly in our "Impact Case Studies" submission too &ndash; over 50% are 4*

]
]

---

count: false
# UCL Department of Statistical Science

.left-column[
`r include_fig("UCL_Stats_logo.jpeg",width="100%")`
]

.font115[
.right-column[
`r vspace("-30px")`

## History

- First ever Department of Statistics in the world; founded in 1911

- Its first head was Karl Pearson (more on this later...)

- Now one of the largest in the UK


## Active in research

- Wide variety of statistical research

- 90% of research outputs submitted in the "Research Excellence Framework" (REF; 2021) ranked as "**internationally excellent**"

- We've improved markedly in our "Impact Case Studies" submission too &ndash; over 50% are 4*


## Friendly department

- About 50 academic staff

- Over 600 undergraduate students and about 150 postgraduate students

- Teaching carried out by staff at the forefront of their subject

- We even have our own `r paste0('&nbsp;<a href="https://twitter.com/stats_UCL"; title="Follow us on twitter (@stats_UCL)">',fontawesome::fa("x-twitter",fill="black",height="0.8em"),'</a>&nbsp;')`, `r paste0('&nbsp;<a href="https://www.linkedin.com/in/statistical-science-ucl-906b9a201"; title="Follow us on LinkedIn">',icons::icon_style(icons::fontawesome("linkedin"),scale=.8,fill="#0077b5",bottom="1em"),'</a>&nbsp;')`,  `r paste0('&nbsp;<a href="https://www.instagram.com/ucl.stats/"; title="Follow us on Instagram">',icons::icon_style(icons::fontawesome("instagram-square"),scale=.8,bottom="1em"),'</a>&nbsp;')`, [magazine](https://www.ucl.ac.uk/statistics/news/2020/apr/sample-space-issue-1-spring-2020) and [podcast](https://soundcloud.com/uclsound/sets/sample-space)! 
]
]

---

# Random talks 

`r include_fig("soundcloud-tom.png",width="65%")`

.footnote[
Check this out on our podcast [https://soundcloud.com/uclsound/sets/sample-space](https://soundcloud.com/uclsound/sets/sample-space)
]

---

# Sample space

[https://sample-space.org](https://sample-space.org)

<iframe frameborder="no" src="https://sample-space.org/"
style="
    position: fixed;
    top: -40px;
    bottom: 0px;
    right: 0px;
    left: -0px;
    width: 120%;
    border: none;
    margin: 0;
    padding: 0;
    overflow: hidden;
    z-index: 999999;
    height: 120%;
    ms-transform: scale(0.45);
   -moz-transform: scale(0.45);
   -o-transform: scale(0.45);
   -webkit-transform: scale(0.45);
   transform: scale(0.65);
  "></iframe>

```{r, echo=FALSE, out.width="100%",out.extra='style="border: none;"',eval=FALSE}
knitr::include_url("https://sample-space.org/", height="600px")
```

---

class: thankyou-michelle 
