---
title: "UCL Maths & Stats"
author: Gianluca Baio
institute: "[Department of Statistical Science](https://www.ucl.ac.uk/statistics/) | University College London"
params: 
   conference: "Martingale Foundation Open Day"
   location: " Royal Institution, London"
   date: 8 December 2023
   short_title: "Martingale Open Day"
   center_footer: TRUE
   slides_url: ""
date: 
output:
  xaringan::moon_reader:
    # This allows to use the local 'remarks' installation, obtained by running 'xaringan::summon_remarks()'
    # chakra: libs/remark-latest.min.js
    includes: 
       in_header: "assets/latex_macros.html" 
       ## This line adds a logo based on the format selected in the file 'assets/THEME/include_logo.html'
       ## NB: the actual options (eg placement of the logo and actual logo file) can be changed there
       ## There's also a script to manipulate the colouring scheme for the UCL logo (from a basic black/white one)
       after_body: "assets/ucl-stats/insert-logo.html"
    seal: false
    yolo: no
    lib_dir: libs
    nature:
      beforeInit: ["https://platform.twitter.com/widgets.js"]
      highlightStyle: github
      highlightLines: yes
      countIncrementalSlides: no
      ratio: '16:9'
      titleSlideClass:
      - center
      - middle
    self_contained: false 
    css:
    - "assets/fonts.css"
    - "assets/ucl-stats.css"
    - "assets/common.css"
---

```{r echo=F,message=FALSE,warning=FALSE,comment=NA}
# Sources the R file with all the relevant setup and commands
source("assets/setup.R")

# Stuff from 'xaringanExtra' (https://pkg.garrickadenbuie.com/xaringanExtra)
# This allows the use of panels (from 'xaringanExtra')
xaringanExtra::use_panelset()
# This allows to copy code from the slides directly
xaringanExtra::use_clipboard()
# This freezes the frame for when there's a gif included
xaringanExtra::use_freezeframe()
# Can also add the scribbling function to the slides
# xaringanExtra::use_scribble()
# Can also add a search box
# xaringanExtra::use_search(show_icon = TRUE)

# Defines the path to the file with the .bib entries (in case there are references)
bibfile=ReadBib("~/Dropbox/Perso/Office/CV/mypubs.bib",check = FALSE)
```

```{r title-page, child="assets/title-page.Rmd"}
```

# University College London

<style>
.font125 {
font-size: 125%;
}
.left-35 {
  width: 35%;
  height: 92%;
  float: left;
}
.left-35 h2, .left-column h3 {
  color: #035AA699;
}
.left-35 h2:last-of-type, .left-column h3:last-child {
  color: #035AA6;
}
.right-65 {
  width: 60%;
  float: right;
  padding-top: 0em;
}
</style>

`r vspace("50px")`
.left-35[
`r vspace("30px")`
`r include_fig("ucl-portico-ranbow.jpg",width="100%")`
]

.right-65[
.font125[
- UCL is a part of the [University of London](https://london.ac.uk/)

   - UoL is a **federation** of 17 independent member institutions of outstanding global reputation

`r vspace("30px")`
   
- We are a multidisciplinary university in its own right

- Founded in 1826 (you'll be bang in the middle of the bicentenary celebrations!)

- The first English university to admit Jewish, Catholics, Non-conformists faiths, Women, ...

   - [Thomas Arnold](https://en.wikipedia.org/wiki/Thomas_Arnold) referred to us as "*that Godless institution in Gower Street*".

`r vspace("30px")`

- The first globally to have departments of **Statistics**, Economics, Modern Languages, ...

]
]

---

count: false
# University College London

`r vspace("50px")`
.left-35[
`r vspace("30px")`
`r include_fig("ucl-portico-ranbow.jpg",width="100%")`
]

.right-65[
.font125[
- UCL is a part of the [University of London](https://london.ac.uk/)

   - UoL is a **federation** of 17 independent member institutions of outstanding global reputation

`r vspace("30px")`
   
- We are a multidisciplinary university in its own right

- Founded in 1826 (you'll be bang in the middle of the bicentenary celebrations!)

- The first English university to admit Jewish, Catholics, Non-conformists faiths, Women, ...

   - [Thomas Arnold](https://en.wikipedia.org/wiki/Thomas_Arnold) referred to us as "*that Godless institution in Gower Street*".

`r vspace("30px")`

- The first globally to have departments of **Statistics**, Economics, Modern Languages, ...

`r vspace("20px")`
- ... And, of course, one of the founding Martingale's partners
]
]

---

# UCL Department of Mathematics

.left-column[
`r include_fig("maths.jpg",width="100%")`
]

.right-column[
`r vspace("-30px")`
## History

- The Department of Mathematics goes back to 1826 as one of the founding departments of UCL
- It is the third oldest mathematics department in England

]

---

count: false

# UCL Department of Mathematics

.left-column[
`r include_fig("maths.jpg",width="100%")`
]

.right-column[
`r vspace("-30px")`
## History

- The Department of Mathematics goes back to 1826 as one of the founding departments of UCL
- It is the third oldest mathematics department in England


## Notable staff

- De Morgan, Sylvester, Hill, Davenport, Clifford, Lighthill, Roth, Baker, Gowers and many others
- Susan Brown, in 1986, became one of the first female professors in mathematics in the UK
- Helen Wilson (former Head of Department) was president of the British Society of Rheology (2015–2017) , the first female to hold this position
]

---

count: false

# UCL Department of Mathematics

.left-column[
`r include_fig("maths.jpg",width="100%")`
]

.right-column[
`r vspace("-30px")`
## History

- The Department of Mathematics goes back to 1826 as one of the founding departments of UCL
- It is the third oldest mathematics department in England


## Notable staff

- De Morgan, Sylvester, Hill, Davenport, Clifford, Lighthill, Roth, Baker, Gowers and many others
- Susan Brown, in 1986, became one of the first female professors in mathematics in the UK
- Helen Wilson (former Head of Department) was president of the British Society of Rheology (2015–2017) , the first female to hold this position

## The department today

- About 70 academic staff, almost 30 full professors, supported by 20 PS staff active research in many areas of mathematics, ranging from pure Mathematics like Analysis, Number Theory and Geometry to Fluids Mechanics, Mathematical Biology, Financial Mathematics and many more
- Over 1000 students across all degree programmes, including PhD students very active public engagement during the pandemic by our Clinical Operational Research Unit (CORU)
]

---

# UCL Department of Statistical Science

<style>
.font115 {
font-size: 115%;
}
</style>

.left-column[
`r include_fig("UCL_Stats_logo.jpeg",width="100%")`
]

.font115[
.right-column[
`r vspace("-30px")`
## History

- First ever Department of Statistics in the world; founded in 1911

- Its first head was Karl Pearson (more on this later...)

- Now one of the largest in the UK

]
]

---

count: false
# UCL Department of Statistical Science

.left-column[
`r include_fig("UCL_Stats_logo.jpeg",width="100%")`
]

.font115[
.right-column[
`r vspace("-30px")`
## History

- First ever Department of Statistics in the world; founded in 1911

- Its first head was Karl Pearson (more on this later...)

- Now one of the largest in the UK


## Active in research

- Wide variety of statistical research

- 90% of research outputs submitted in the "Research Excellence Framework" (REF; 2021) ranked as "**internationally excellent**"

- We've improved markedly in our "Impact Case Studies" submission too &ndash; over 50% are 4*

]
]

---

count: false
# UCL Department of Statistical Science

.left-column[
`r include_fig("UCL_Stats_logo.jpeg",width="100%")`
]

.font115[
.right-column[
`r vspace("-30px")`

## History

- First ever Department of Statistics in the world; founded in 1911

- Its first head was Karl Pearson (more on this later...)

- Now one of the largest in the UK


## Active in research

- Wide variety of statistical research

- 90% of research outputs submitted in the "Research Excellence Framework" (REF; 2021) ranked as "**internationally excellent**"

- We've improved markedly in our "Impact Case Studies" submission too &ndash; over 50% are 4*


## Friendly department

- About 50 academic staff

- Over 600 undergraduate students and about 150 postgraduate students

- Teaching carried out by staff at the forefront of their subject

- We even have our own `r paste0('&nbsp;<a href="https://twitter.com/stats_UCL"; title="Follow us on twitter (@stats_UCL)">',fontawesome::fa("x-twitter",fill="black",height="0.8em"),'</a>&nbsp;')`, `r paste0('&nbsp;<a href="https://www.linkedin.com/in/statistical-science-ucl-906b9a201"; title="Follow us on LinkedIn">',icons::icon_style(icons::fontawesome("linkedin"),scale=.8,fill="#0077b5",bottom="1em"),'</a>&nbsp;')`,  `r paste0('&nbsp;<a href="https://www.instagram.com/ucl.stats/"; title="Follow us on Instagram">',icons::icon_style(icons::fontawesome("instagram-square"),scale=.8,bottom="1em"),'</a>&nbsp;')`, [magazine](https://www.ucl.ac.uk/statistics/news/2020/apr/sample-space-issue-1-spring-2020) and [podcast](https://soundcloud.com/uclsound/sets/sample-space)! 
]
]

---

# Random talks 

`r include_fig("soundcloud-tom.png",width="65%")`

.footnote[
Check this out on our podcast [https://soundcloud.com/uclsound/sets/sample-space](https://soundcloud.com/uclsound/sets/sample-space)
]

---

# Chalkdust

[https://chalkdustmagazine.com/](https://chalkdustmagazine.com/)

```{r, echo=FALSE, out.width="100%",out.extra='style="border: none;"',eval=TRUE}
knitr::include_url("https://chalkdustmagazine.com/", height="600px")
```

---

# Sample space

[https://sample-space.org](https://sample-space.org)


```{r, echo=FALSE, out.width="100%",out.extra='style="border: none;"',eval=TRUE}
knitr::include_url("https://sample-space.org/", height="600px")
```

---

# Your pathway at UCL

.content-box-beamer[
## [MSc in Mathematical Modelling](https://www.ucl.ac.uk/prospective-students/graduate/taught-degrees/mathematical-modelling-msc)

- This MSc provides an ideal foundation for students wishing to advance their mathematical modelling skills. The programme teaches students the basic concepts which arise in a broad range of technical and scientific problems and illustrates how these may be applied in a research context to provide powerful solutions.

- Students develop an understanding of the processes undertaken to arrive at a suitable mathematical model and are taught the fundamental analytical techniques and computational methods used to develop insight into system behaviour. The programme introduces a range of problems - industrial, biological and environmental - and associated conceptual models and solutions.
]

--

.content-box-beamer[
## [MSc in Data Science](https://www.ucl.ac.uk/prospective-students/graduate/taught-degrees/data-science-msc)

- Data science brings together computational and statistical skills for data-driven problem solving. This programme will equip students with the analytical tools to design sophisticated technical solutions using modern computational methods and with an emphasis on rigorous statistical thinking. 

- The programme combines training in core statistical and machine learning methodology, beginning at an introductory level, with a range of optional modules covering more specialised knowledge in statistical computing and modelling. Students will take one compulsory module and up to two additional modules in computer science, with the remaining modules (including the research project) taken mainly from within statistical science.
]

--

.content-box-beamer[
## [MSc in Statistics](https://www.ucl.ac.uk/prospective-students/graduate/taught-degrees/statistics-msc)

- Statistical science skills are powerful tools that play a valuable role in all pure and applied sciences as well as in finance, commerce and medicine. The quantitative skills training provided by this MSc can lead to new and exciting opportunities in industry, healthcare, government, commerce or research.

- The programme takes a broad-based approach to statistics, providing up-to-date training in the major applications and an excellent balance between theory and application. It covers modern ideas in statistics including applied Bayesian methods, generalised linear modelling and object-oriented statistical computing, together with a grounding in traditional statistical theory and methods.
]

---

count: false
# Your pathway at UCL

We work at the forefront of the mathematical sciences, providing the foundations for many scientific, technological and social advances
`r vspace("30pt")`

1. Foundational Data Science and its applications

   - Environmental sciences (partnership with the MetOffice)
   - Biomedical sciences (links with UCLH, IoN and others)
`r vspace("20pt")`

2. Machine learning and (the ethical and sensible use of) artificial intelligence
`r vspace("20pt")`

3. Mathematical and statistical modelling for financial applications
`r vspace("20pt")`

4. Computational methods

  - Bayesian computation and applications to a wide range of areas
`r vspace("20pt")`

5. Mathematical and statistical modelling for decision-making

   - Economic evaluation of intervention
   - Causal inference
`r vspace("20pt")`

6. Probability theory

---

class: thankyou-michelle 
